Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-24 icse/paper.tex
Some stuff

Based on these relations, CloneRefactor determines where to place the cloned code when refactored. The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class. The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor). The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface, but in the process has to become part of the classes' public contract. The code of clones that are \textit{Unrelated} can be placed in a newly created place: either a utility class, a new superclass abstraction or an interface.

@@

\subsection{Extract Method}
%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique. The second column shows our measurements for the complete systems (just like the former experiments). The third column shows our measurements when restricting our search to method bodies. The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).

\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\%}} \\ \midrule
Can Be Extracted & 24,157 & 28.2\%  \\
Is Not A Partial Method & 21,625 & 25.3\% \\
Top-level AST-Node is not a Statement & 19,887 & 23.2\% \\
Spans Part of a Block & 12,964 & 15.2\%  \\
Multiple Return Values & 5,622 & 6.6\%  \\
Complex Control Flow & 1,106 & 1.3\% \\
Overlap In Clone Class & 147 & 0.2\% \\
Not In Class Or Interface & 70 & 0.1\% \\
\end{tabular}
\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
\label{tab:refactorability}
\end{table}

@@

The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code. Because of that, for our further experiments, we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.

>>>>

Based on these relations, CloneRefactor determines where to place the cloned code when refactored. These categories are mutually exclusive: a clone class will be flagged as the first relation in above list that it applies to. The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class. The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor). The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface, but in the process has to become part of the classes' public contract. The code of clones that are \textit{Unrelated} can be placed in a newly created place: either a utility class, a new superclass abstraction or an interface.

@@

\subsection{Extract Method}
%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique (see ). %The second column shows our measurements for the complete systems (just like the former experiments). %The third column shows our measurements when restricting our search to method bodies. The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).

\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\%}} \\ \midrule
Can Be Extracted & 24,157 & 28.2\%  \\
Is Not A Partial Method & 21,625 & 25.3\% \\
Top-level AST-Node is not a Statement & 19,887 & 23.2\% \\
Spans Part of a Block & 13,181 & 15.5\%  \\
Multiple Return Values & 5,622 & 6.6\%  \\
Complex Control Flow & 1,106 & 1.3\% \\
\end{tabular}
\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique.}
\label{tab:refactorability}
\end{table}

@@
